Baker, Malcolm, and Jeffrey Wurgler. "Investor sentiment in the stock market." The Journal of Economic \hspace*{8ex}Perspectives 21.2 (2007): 129-151.

Bollen, Johan, Huina Mao, and Xiaojun Zeng. "Twitter mood predicts the stock market." Journal of \hspace*{8ex}computational science 2.1 (2011): 1-8.

Brown, Gregory W. and Michael T. Cliff. "Investor Sentiment And The Near-Term Stock Market". \hspace*{8ex}Journal of Empirical Finance 11.1 (2004): 1-27.

Chen, Ray, and Marius Lazer. "Sentiment analysis of twitter feeds for the prediction of stock market \hspace*{8ex}movement." stanford. edu. Retrieved January 25 (2013): 2013.

Chui, Andy C.W., Titman, Sheridan and Wei, K.C. John, (2010), Individualism and Momentum around \hspace*{8ex}the World, Journal of Finance, 65, issue 1, p. 361-392, http://EconPapers.repec.org/RePEc:bla:jfi\\\hspace*{8ex}nan:v:65:y:2010:i:1:p:361-392.

Clarke, Roger G., and Meir Statman. "Bullish or bearish?."Financial Analysts Journal(1998): 63-72.

Dergiades, Theologos. "Do Investors’ Sentiment Dynamics Affect Stock Returns? Evidence From The \hspace*{8ex}US Economy".Economics Letters116.3 (2012): 404-407. Web.

Fisher, Kenneth L. and Meir Statman. "Investor Sentiment And Stock Returns". Financial Analysts \hspace*{8ex}Journal 56.2 (2000): 16-23.

Giot, Pierre. "Relationships between implied volatility indexes and stock index returns." The Journal of \hspace*{8ex}Portfolio Management 31.3 (2005): 92-100.

Hofstede, Geert. "Culture's recent consequences: Using dimension scores in theory and research." \hspace*{8ex}International Journal of cross cultural management 1.1 (2001): 11-17.

Lemmon, Michael, and Evgenia Portniaguina. "Consumer confidence and asset prices: Some empirical \hspace*{8ex}evidence." Review of Financial Studies 19.4 (2006): 1499-1529.

Liu, Shuming. "Investor Sentiment And Stock Market Liquidity". Journal of Behavioral Finance 16.1 \hspace*{8ex}(2015): 51-67. Web.

Rao, Tushar, and Saket Srivastava. "Analyzing stock market movements using twitter sentiment \\\hspace*{8ex}analysis." Proceedings of the 2012 International Conference on Advances in Social Networks \hspace*{8ex}Analysis and Mining (ASONAM 2012). IEEE Computer Society, 2012.

Simon, David P., and Roy A. Wiggins. "S\&P futures returns and contrary sentiment indicators." Journal \hspace*{8ex}of futures markets 21.5 (2001): 447-462.

Skuza, Michał, and Andrzej Romanowski. "Sentiment analysis of Twitter data within big data \\\hspace*{8ex}distributed environment for stock prediction." Computer Science and Information Systems \\\hspace*{8ex}(FedCSIS), 2015 Federated Conference on. IEEE, 2015.

Smales, L.A. "The Importance Of Fear: Investor Sentiment And Stock Market Returns".Applied Eco\\\hspace*{8ex}nomics(2017): 1-27. Web.

Solt, Michael E., and Meir Statman. "How useful is the sentiment index?."Financial Analysts Journal\\\hspace*{8ex}(1988): 45-55.

Tetlock, Paul C. "Giving content to investor sentiment: The role of media in the stock market." The \hspace*{8ex}Journal of Finance 62.3 (2007): 1139-1168.

Whaley, Robert E. "The investor fear gauge." The Journal of Portfolio Management 26.3 (2000): 12-17
